cvx-flats

### 2020-05-19 neurips-20/cvx-flats-statements.tex
Minor tweak in proof of Lemma 5

\jessie{D $\implies$ A}
	First, we can verify that $\zeta$ as constructed maps $\zeta(0) = 0$ and is continuous at $0$.	
	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, we note that $\zeta(0) = \sup_{u':R_L(u;p) = 0} (R_\ell(\psi(u'); p)) = \sup_{u' \in \Gamma(p)} (R_\ell(\psi(u'); p))$.
	If there is a $u \in \Gamma(p)$ so that $R_\ell(\psi(u); p) > \risk{\ell}(p)$, then the constant sequence $\{u_m\} = u$ for all $m$ has $R_L(u_m;p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, thus we must have $\zeta(0) = 0$.

>>>>

\jessie{D $\implies$ A}
	First, we can verify that $\zeta$ as constructed maps $\zeta(0) = 0$ and is continuous at $0$.	
	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, we note that $\zeta(0) = \sup_{u':R_L(u;p) = 0} (R_\ell(\psi(u'); p)) = \sup_{u' \in \Gamma(p)} (R_\ell(\psi(u'); p))$.
	If there is a $u \in \Gamma(p)$ so that $R_\ell(\psi(u); p) > \risk{\ell}(p)$ (i.e. $\zeta(0) > 0$), then the constant sequence $\{u_m\} = u$ for all $m$ gives $R_L(u_m;p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, yielding a contradiction; therefore, we must have $\zeta(0) = 0$.
